---
title: "How Many Movies Pass the Bechdel Test Each Year?"
output: github_document
---

```{r setup, include=FALSE, results='hide'}
knitr::opts_chunk$set(echo = FALSE)
```

Based on data from [**FiveThirtyEight.**](https://fivethirtyeight.com/features/the-dollar-and-cents-case-against-hollywoods-exclusion-of-women/)

Named for the cartoonist Alison Bechdel, the Bechdel Test is a measure of the representation of women in media. In order for a film to pass the test, Bechdel had three criteria: 1) there must be at least two named women in the film, 2) they must have a conversation with each other at some point, and 3) that conversation can't be about a male character. 

This data set analyzes 1,794 films released between 1970 and 2013. 
```{r, echo=FALSE, results='hide', message=FALSE}
library(ggplot2)
library(dplyr)
library(fivethirtyeight)

bechdel_edits <- bechdel %>% 
  group_by(year, binary) %>% 
  summarize(count = n())
  
```



```{r pressure, echo=FALSE}
ggplot(data=bechdel_edits, mapping=aes(x=year, y=count, color=binary)) +
  geom_line() +
  labs(x="Year", y="Number of movies") +
  ggtitle("Movies and the Bechdel Test Over Time")
```

